6.867 Problem Set 3

### 2015-11-11 HW3/tex/HW3.tex
[hw3] toy data set plots.
[hw3] table setup.

@@

\begin{table}
\captionof{table}{Performance of neural network with stochastic gradient descent on Toy Data Set 1 (training)} 
\centering
\begin{tabular}{llllll}
\toprule
& $n_1$ = \bf{1} & $n_1$ =  \bf{3} & $n_1$ =  \bf{5} & $n_1$ =  \bf{7} & $n_1$ =  \bf{9} \\
\midrule
$\lambda$ = \bf{0} &       0.003 & \bf{0.003} & 0.003 & 0.003 & 0.003 \\
$\lambda$ = \bf{1e-5} &   0.037 & 0.003 & 0.003 & 0.003 & 0.003 \\
$\lambda$ = \bf{1e-3} &   0.333 & 0.003 & 0     & 0.003 & 0.003 \\
$\lambda$ = \bf{1e-1} &   0.667 & 0.667 & 0.667 & 0.667 & 0.667 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\captionof{table}{Performance of neural network with stochastic gradient descent on Toy Data Set 1 (validation)} 
\centering
\begin{tabular}{llllll}
\toprule
& $n_1$ = \bf{1} & $n_1$ =  \bf{3} & $n_1$ =  \bf{5} & $n_1$ =  \bf{7} & $n_1$ =  \bf{9} \\
\midrule
$\lambda$ = \bf{0} &        0.01  & \bf{0.003} & 0.003 & 0.003 & 0.003 \\
$\lambda$ = \bf{1e-5} &    0.03  & 0.003 & 0.007 & 0.003 & 0.007 \\
$\lambda$ = \bf{1e-3} &    0.333 & 0.007 & 0.01  & 0.01  & 0.017 \\
$\lambda$ = \bf{1e-1} &    0.667 & 0.667 & 0.667 & 0.667 & 0.667 \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{table}
\captionof{table}{Performance of neural network with stochastic gradient descent on Toy Data Set 2 (training)} 
\centering
\begin{tabular}{llllll}
\toprule
& $n_1$ = \bf{1} & $n_1$ =  \bf{3} & $n_1$ =  \bf{5} & $n_1$ =  \bf{7} & $n_1$ =  \bf{9} \\
\midrule
$\lambda$ = \bf{0} &       0.367 & 0.077 & 0.063 & 0.057 & 0.05  \\
$\lambda$ = \bf{1e-5} &   0.363 & 0.073 & \bf{0.067} & 0.063 & 0.063 \\
$\lambda$ = \bf{1e-3} &   0.357 & 0.087 & 0.083 & 0.083 & 0.09  \\
$\lambda$ = \bf{1e-1} &   0.667 & 0.667 & 0.667 & 0.667 & 0.667 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\captionof{table}{Performance of neural network with stochastic gradient descent on Toy Data Set 2 (validation)} 
\centering
\begin{tabular}{llllll}
\toprule
& $n_1$ = \bf{1} & $n_1$ =  \bf{3} & $n_1$ =  \bf{5} & $n_1$ =  \bf{7} & $n_1$ =  \bf{9} \\
\midrule
$\lambda$ = \bf{0} &        0.373 & 0.097 & 0.11  & 0.117 & 0.113 \\
$\lambda$ = \bf{1e-5} &    0.373 & 0.103 & \bf{0.09}  & 0.09  & 0.09  \\
$\lambda$ = \bf{1e-3} &    0.37  & 0.107 & 0.103 & 0.103 & 0.103 \\
$\lambda$ = \bf{1e-1} &    0.667 & 0.667 & 0.667 & 0.667 & 0.667 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{figure}[ht]
	\centering
	\begin{minipage}[b]{.48\linewidth}
		\includegraphics[width=1\linewidth, height=2.7in]{t1dist.jpg}
		\caption*{Toy Dataset \#1}
	\end{minipage}
	\begin{minipage}[b]{.48\linewidth}
		\includegraphics[width=1\linewidth, height=2.7in]{t2dist.jpg}
		\caption*{Toy Dataset \#2}
	\end{minipage}
	\caption{Distributions of different classes in $X1$, $X2$ for toy datasets}
\end{figure}

@@

\begin{table}
\captionof{table}{Performance of neural network with stochastic gradient descent on Toy Data Set 1 (training)} 
\centering
\begin{tabular}{llllll}
\toprule
& $n_1$ = \bf{1} & $n_1$ =  \bf{3} & $n_1$ =  \bf{5} & $n_1$ =  \bf{7} & $n_1$ =  \bf{9} \\
\midrule
$\lambda$ = \bf{0} &       \bf{0.003} & 0.003 & 0.003 & 0.003 & 0.003 \\
$\lambda$ = \bf{1e-5} &   0.043 & 0     & 0.003 & 0.003 & 0     \\
$\lambda$ = \bf{1e-3} &   0.117 & 0     & 0.003 & 0.003 & 0.003 \\
$\lambda$ = \bf{1e-1} &   0.667 & 0.667 & 0.667 & 0.667 & 0.667 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\captionof{table}{Performance of neural network with stochastic gradient descent on Toy Data Set 1 (validation)} 
\centering
\begin{tabular}{llllll}
\toprule
& $n_1$ = \bf{1} & $n_1$ =  \bf{3} & $n_1$ =  \bf{5} & $n_1$ =  \bf{7} & $n_1$ =  \bf{9} \\
\midrule
$\lambda$ = \bf{0} &        \bf{0.003} & 0.003 & 0.01  & 0.007 & 0.003 \\
$\lambda$ = \bf{1e-5} &    0.033 & 0.007 & 0.003 & 0.007 & 0.003 \\
$\lambda$ = \bf{1e-3} &    0.097 & 0.013 & 0.013 & 0.013 & 0.013 \\
$\lambda$ = \bf{1e-1} &    0.667 & 0.667 & 0.667 & 0.667 & 0.667 \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{table}
\captionof{table}{Performance of neural network with stochastic gradient descent on Toy Data Set 2 (training)} 
\centering
\begin{tabular}{llllll}
\toprule
& $n_1$ = \bf{1} & $n_1$ =  \bf{3} & $n_1$ =  \bf{5} & $n_1$ =  \bf{7} & $n_1$ =  \bf{9} \\
\midrule
$\lambda$ = \bf{0} &       0.363 & 0.073 & 0.053 & 0.05  & 0.06  \\
$\lambda$ = \bf{1e-5} &   0.363 & 0.07  & \bf{0.067} & 0.057 & 0.067 \\
$\lambda$ = \bf{1e-3} &   0.363 & 0.07  & 0.07  & 0.07  & 0.07  \\
$\lambda$ = \bf{1e-1} &   0.667 & 0.667 & 0.667 & 0.667 & 0.667 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\captionof{table}{Performance of neural network with stochastic gradient descent on Toy Data Set 2 (validation)} 
\centering
\begin{tabular}{llllll}
\toprule
& $n_1$ = \bf{1} & $n_1$ =  \bf{3} & $n_1$ =  \bf{5} & $n_1$ =  \bf{7} & $n_1$ =  \bf{9} \\
\midrule
$\lambda$ = \bf{0} &        0.373 & 0.083 & 0.11  & 0.103 & 0.113 \\
$\lambda$ = \bf{1e-5} &    0.373 & 0.087 & \bf{0.077} & 0.08  & 0.09  \\
$\lambda$ = \bf{1e-3} &    0.377 & 0.097 & 0.097 & 0.093 & 0.093 \\
$\lambda$ = \bf{1e-1} &    0.667 & 0.667 & 0.667 & 0.667 & 0.667 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\captionof{table}{Neural Net Performance on MNIST dataset for different choices of parameters} 
\centering
\begin{tabular}{llllll}
\toprule
& $n_1$ = 50 & $n_1$ = 100 & $n_1 = 150$ \\
\midrule
Training, $lr = .1$, full gradient descent, $\lambda$ = 0 & && \\
Training, $lr = .1$, full gradient descent, $\lambda$= 1e-3 & && \\
Training, $lr = .1$, full gradient descent, $\lambda$= 1e-2 & && \\
Training, $lr = .1$, full gradient descent, $\lambda$= 1e-1 & && \\
Validation, $lr = .1$, full gradient descent, $\lambda$ = 0 & && \\
Validation, $lr = .1$, full gradient descent, $\lambda$= 1e-3 & && \\
Validation, $lr = .1$, full gradient descent, $\lambda$= 1e-2 & && \\
Validation, $lr = .1$, full gradient descent, $\lambda$= 1e-1 & && \\
Training, $lr = .1$, SGD, $\lambda$ = 0 & && \\
Training, $lr = .1$, SGD, $\lambda$= 1e-3 & && \\
Training, $lr = .1$, SGD, $\lambda$= 1e-2 & && \\
Training, $lr = .1$, SGD, $\lambda$= 1e-1 & && \\
Validation, $lr = .1$, SGD, $\lambda$ = 0 & && \\
Validation, $lr = .1$, SGD, $\lambda$= 1e-3 & && \\
Validation, $lr = .1$, SGD, $\lambda$= 1e-2 & && \\
Validation, $lr = .1$, SGD, $\lambda$= 1e-1 & && \\
Training, $lr = .01$, full gradient descent, $\lambda$ = 0 & && \\
Training, $lr = .01$, full gradient descent, $\lambda$= 1e-3 & && \\
Training, $lr = .01$, full gradient descent, $\lambda$= 1e-2 & && \\
Training, $lr = .01$, full gradient descent, $\lambda$= 1e-1 & && \\
Validation, $lr = .01$, full gradient descent, $\lambda$ = 0 & && \\
Validation, $lr = .01$, full gradient descent, $\lambda$= 1e-3 & && \\
Validation, $lr = .01$, full gradient descent, $\lambda$= 1e-2 & && \\
Validation, $lr = .01$, full gradient descent, $\lambda$= 1e-1 & && \\
Training, $lr = .01$, SGD, $\lambda$ = 0 & && \\
Training, $lr = .01$, SGD, $\lambda$= 1e-3 & && \\
Training, $lr = .01$, SGD, $\lambda$= 1e-2 & && \\
Training, $lr = .01$, SGD, $\lambda$= 1e-1 & && \\
Validation, $lr = .01$, SGD, $\lambda$ = 0 & && \\
Validation, $lr = .01$, SGD, $\lambda$= 1e-3 & && \\
Validation, $lr = .01$, SGD, $\lambda$= 1e-2 & && \\
Validation, $lr = .01$, SGD, $\lambda$= 1e-1 & && \\
\bottomrule
\end{tabular}
\end{table}
